# Rmarkdown Cheatsheet


# Analysis of the cars dataset in R
## By Narendra Roy

**Part 1**

<!-- Anything after 3 ` and {r} is R code scope and the scope ends with 3 ` -->

```{r eval=FALSE}

data(cars)
str(cars)
summary(cars)
plot(cars)

```

<!-- This is comment -->
<!-- For in-line evaluation of R code: -->
There were `r nrow(cars)` cars studied

http://example.com

[linked phrase](http://example.com)

__Unordered list__
* Item
* Item 2
    + Item 2a
    + Item 2b
   
__Ordered List__
1. Item 1
2. Item 2
3. Item 3
    + Item 3a
    + Item 3b
    
eval is false therefore, you won't see any warning message or any output

```{r eval=FALSE}    
library(caret)
```

A friend once said:

> It's always better to give 
> than to receive.


Plain code blocks are displayed in a fixed-width font but not evaulated
```
This text is displayed verbatim / preformatted
```

__Links__
A [linked phrase][id]. 

At the bottom of the document:

[id]: http://example.com/ "Title"

__Miscellaneous__

superscript^2^

subscript~2~

~~strikethrough~~

__Images__

![alt text][id] At the bottom of the document:

[id]: image.jpg "Title"


__Emphasis__


*italic*   **bold**

_italic_   __bold__

__Headers__

# Header 1

## Header 2

### Header 3
